Miniproject - Algebraic Geometry

### 2021-12-19 Algebraic geometry/submission.tex
Done last proofreading of alg geo

In this Miniproject, we want to study the Grassmanian
\begin{equation*}
    \Gr(d, V) := \{ U \subseteq V \ | \ U \ \text{$d$-dimensional subspace} \}
\end{equation*}
as an object of Algebraic Geometry.
First of all, this requires finding a ``natural'' embedding of $\Gr(d, V)$ in to projective space, and showing that w.r.t. that embedding, the Grassmanian is a projective variety.

After that is established, we can continue to study its geometric properties, like vanishing ideal, dimension and degree.
This part will only be considered in the case $d = 2$.

@@

\section{Part I}
First of all, I will include here a more formal definition of the exterior product, which is required for rigorous proofs later on.
\begin{definition}
    Define the $d$-th exterior power of $V$ as a quotient of the free vector space of $B \times ... \times B$ as follows
    \begin{align*}
        \extpow^d V := \mathrm{Fr}\Bigl(\bigtimes_{i = 1}^d B\Bigr) \ \bigm/ \ U
    \end{align*}
    where
    \begin{align*}
        U = \vspan \bigl\{ (v_1, ..., v_d) + (v_1, ..., v_{i - 1}, v_{i + 1}, v_i, v_{i + 2}, ..., v_d) \ \bigm| \ v_1, ..., v_d \in B, 1 \leq i < d \bigr\}
    \end{align*}
    Consider also the map
    \begin{equation*}
        \wedge: \bigtimes_{i = 1}^d V \to \extpow^d V, \quad \Bigl( \sum_{i = 1}^n \lambda_{1i} b_i, ..., \sum_{i = 1}^n \lambda_{di} b_i \Bigr) \mapsto \sum_{1 \leq i_1, ..., i_d \leq n} \lambda_{1i_1} ... \lambda_{di_d} (b_{i_1}, ..., b_{i_d})
    \end{equation*}
    and use the notation $v_1 \wedge ... \wedge v_d$ to denote the image of $(v_1, ..., v_d)$ under this map.
\end{definition}
First of all, we show some basic properties of the exterior product.
It is straightforward to see that the exterior product is multilinear, i.e. $v_1 \wedge ... \wedge (v_i + v'_i) \wedge ... \wedge v_d = (v_1 \wedge ... \wedge v_d) + (v_1 \wedge ... \wedge v'_i \wedge ... \wedge v_d)$.
More interesting are the following properties.
\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Clearly the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ span $\extpow^d V$.
    So let
    \begin{equation*}
        u = \sum_{i_1, ..., i_{j - 1}} \lambda_{i_1, ..., i_{j - 1}} (b_1 \wedge ... \wedge b_{j - 1}), \quad w = \sum_{i_1, ..., i_{d - j - 1}} \mu_{i_1, ..., i_d} (b_{i_1} \wedge ... \wedge b_{d - j - 1})
    \end{equation*}
    be arbitrary vectors in $\extpow^{j - 1} V$ resp. $\extpow^{d - j - 1} V$ for some $1 \leq j \leq d - 1$.
    Note that for $v = \sum \tau_i b_i, v' = \sum \tau'_i b_i \in V$ have then
    \begin{align*}
        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \quad \sum_{0 \leq i, i' \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_i \tau'_{i'} \\
        &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ... \wedge b_{i_j} \wedge b_{i_{j + 1}} \wedge ... \wedge b_{i_d}\bigr) + \bigl( b_{i_1} \wedge ... \wedge b_{i_{j - 1}} \wedge b_{i_{j + 1}} \wedge b_{i_j} \wedge b_{i_{j + 2}} \wedge ... \wedge b_{i_d} \bigr)}_{= 0 \ \text{as it is an element of the space $U$}} \Bigl) \\
        &= 0
    \end{align*}
    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V)$.
    Hence
    \begin{equation*}
        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
    \end{equation*}

@@

\begin{lemma}[Question (a)]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
\begin{proof}
    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
    \begin{align*}
        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) - \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
        =& \begin{cases}
            \beta v_1 + \gamma v_2 \wedge \frac \alpha \beta v_2 + v_3 & \text{if $\beta \neq 0$} \\
            \alpha v_1 - \gamma v_3 \wedge v_2 & \text{otherwise}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
    \end{align*}
    are decomposable.
    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
\end{proof}

\begin{example}[Question (b)]
    Consider $V = k^4$. 
    Then the element $w := (e_1 \wedge e_2) + (e_3 \wedge e_4) \in \extpow^2(V)$ is not decomposable. 
\end{example}
\begin{proof}
    Assume it was, then there are $a, b \in k^4$ such that
    \begin{equation*}
        w = \sum_i a_i e_i \wedge \sum_j b_j e_j = \sum_{i < j} (a_i b_j - a_j b_i) (e_i \wedge e_j)
    \end{equation*}
    In other words
    \begin{equation*}
        a_1b_2 - a_2b_1 = 1, \ a_3b_4 - a_4b_3 = 1, \ a_i b_j - a_j b_i = 0 \ \text{for all $(i, j) \neq (1, 2), (3, 4)$}
    \end{equation*}
    Clearly $a_1 b_2 \neq 0$ or $a_2 b_1 \neq 0$.
    Similarly, have $a_3 b_4 \neq 0$ or $a_4 b_3 \neq 0$.
    As all expressions are symmetric w.r.t swapping $a_1, b_2$ with $a_2, b_1$ and $a_3, b_4$ with $a_4, b_3$, we may assume wlog that $a_1 b_2, a_3 b_4 \neq 0$.

@@

    It is left to show that they are linearly independent.
    Assume
    \begin{equation*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1} \wedge ... \wedge b_{i_d} \bigr) = 0
    \end{equation*}
    Then clearly
    \begin{equation*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) \in U
    \end{equation*}
    where $U$ is the vector space from the definition of $\extpow^d V$.
    So
    \begin{align*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) = &\sum_{j, \ i_1, ..., i_d} \mu_{j, i_1, ..., i_d} \\
        &\Bigl( \bigl( b_{i_1}, ..., b_{i_d} \bigr) + \bigl( b_{i_1}, ..., b_{i_{j - 1}}, b_{i_{j + 1}}, b_{i_j}, b_{i_{j + 2}}, ..., b_{i_d} \bigr) \Bigr)
    \end{align*}
    Note that we can assume wlog that the sum on the right-hand side goes only over $i_1, ..., i_d$ distinct.
    The reason is that the other vectors on the right-hand side are contained in
    \begin{equation*}
       \vspan \{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ not distinct} \}
    \end{equation*}
    which only trivially intersects the space
    \begin{equation*}
        \vspan\{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ distinct} \}
    \end{equation*}
    due to the properties of the free product (the spaces share now basis vectors).

@@

        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \underbrace{\bigl( b_{i_1}, ..., b_{i_d} \bigr)}_{\sgn(\sigma_i) = 1 \ \text{as} \ \sigma_i = \mathrm{id}} = &\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \underbrace{\sgn(\sigma_i) \bigl( \mu_{j, i_1, ..., i_d} - \mu_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} \bigr)}_{=: \mu'_{j, i_1, ..., i_d}} \\

@@

            \lambda_{i_1, ..., i_d} & \text{if $i_1 < ... < i_d, j = 0$} \\

@@

    wlog assume that $b_1, ..., b_m$ are a basis of $U$.

@@

        w = \sum_{i_1 < ... < i_{d - 1} < m} \lambda_{i_1, ..., i_{d - 1} \leq m} (b_{i_1} \wedge ... \wedge b_{i_{d - 1}})

@@

        =& \sum_{i_1 \leq n, \ i_1 < ... < i_{d - 1} \leq m} \mu_{i_1} \lambda_{i_2, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})

@@

            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\

@@

        0 = \mu_{i_1}\lambda_{i_2, ..., i_d} - \begin{cases}
            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\
        \end{cases}
    So in particular find for all $i_2 < ... < i_d \leq m < i_1 \leq n$ that

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
    So clearly $v_1 \wedge ... \wedge v_d \neq 0$ as $0 \wedge (v_{d + 1} \wedge ... \wedge v_n) = 0$ for all $v_{d + 1}, ..., v_n \in V$.
\end{proof}
Now we can see that in general, the exterior product contains not decomposable elements.
\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^2 V$.
    Then
    \begin{align*}
        0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
        =& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
    \end{align*}
    Here we used that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).

@@

    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
    To show surjectivity, note that the $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
    Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
    \begin{equation*}
        f(e_{i_1} \wedge ... \wedge e_{i_d})_J = \det(A_J(e_{i_1}, ..., e_{i_j})) = \begin{cases}
            0 & \text{if $J \not\subseteq I$} \\
            \pm 1 & \text{if $J \subseteq I$}
        \end{cases}
    \end{equation*}
    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = k^{\{1, ..., k\}^{(d)}}$.

>>>>

In this Miniproject, we want to study the Grassmanian
\begin{equation*}
    \Gr(d, V) := \{ U \subseteq V \ | \ U \ \text{$d$-dimensional subspace} \}
\end{equation*}
as an object of Algebraic Geometry.
First of all, this requires finding a ``natural'' embedding of $\Gr(d, V)$ into projective space, and showing that w.r.t. that embedding, the Grassmanian is a projective variety.

After that is established, we can continue to study its geometric properties, like vanishing ideal, dimension and degree.
In this part, we will restrict to $d = 2$.

@@

\section{Part I}
First of all, I will include here a more formal definition of the exterior product, which is required for rigorous proofs later on.
\begin{definition}
    Define the $d$-th exterior power of $V$ as a quotient of the free vector space of $B \times ... \times B$ as follows
    \begin{align*}
        \extpow^d V := \mathrm{Fr}\Bigl(\bigtimes_{i = 1}^d B\Bigr) \ \bigm/ \ U
    \end{align*}
    where
    \begin{align*}
        U = \vspan \bigl\{ (v_1, ..., v_d) + (v_1, ..., v_{i - 1}, v_{i + 1}, v_i, v_{i + 2}, ..., v_d) \ \bigm| \ v_1, ..., v_d \in B, 1 \leq i < d \bigr\}
    \end{align*}
    Consider also the map
    \begin{equation*}
        \wedge: \bigtimes_{i = 1}^d V \to \extpow^d V, \quad \Bigl( \sum_{i = 1}^n \lambda_{1i} b_i, ..., \sum_{i = 1}^n \lambda_{di} b_i \Bigr) \mapsto \sum_{1 \leq i_1, ..., i_d \leq n} \lambda_{1i_1} ... \lambda_{di_d} (b_{i_1}, ..., b_{i_d})
    \end{equation*}
    and use the notation $v_1 \wedge ... \wedge v_d$ to denote the image of $(v_1, ..., v_d)$ under this map.
\end{definition}
First of all, we show some basic properties of the exterior product.
It is straightforward to see that the exterior product is multilinear, i.e. $v_1 \wedge ... \wedge (v_i + v'_i) \wedge ... \wedge v_d = (v_1 \wedge ... \wedge v_d) + (v_1 \wedge ... \wedge v'_i \wedge ... \wedge v_d)$.
More interesting are the following properties.
\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Clearly the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ span $\extpow^d V$.
    So let
    \begin{equation*}
        u = \sum_{i_1, ..., i_{j - 1}} \lambda_{i_1, ..., i_{j - 1}} (b_1 \wedge ... \wedge b_{j - 1}), \quad w = \sum_{i_1, ..., i_{d - j - 1}} \mu_{i_1, ..., i_d} (b_{i_1} \wedge ... \wedge b_{d - j - 1})
    \end{equation*}
    be arbitrary vectors in $\extpow^{j - 1} V$ resp. $\extpow^{d - j - 1} V$ for some $1 \leq j \leq d - 1$.
    Note that for $v = \sum \tau_i b_i, v' = \sum \tau'_i b_i \in V$ have then
    \begin{align*}
        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \ \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
        &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ... \wedge b_{i_j} \wedge b_{i_{j + 1}} \wedge ... \wedge b_{i_d}\bigr) + \bigl( b_{i_1} \wedge ... \wedge b_{i_{j - 1}} \wedge b_{i_{j + 1}} \wedge b_{i_j} \wedge b_{i_{j + 2}} \wedge ... \wedge b_{i_d} \bigr)}_{= 0 \ \text{as it is an element of the space $U$}} \Bigl) \\
        &= 0
    \end{align*}
    Hence
    \begin{equation*}
        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
    \end{equation*}

@@

\begin{lemma}[Question (a)]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
\begin{proof}
    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
    \begin{align*}
        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) + \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
        =& \begin{cases}
            (\beta v_1 + \gamma v_2) \wedge (\frac \alpha \beta v_2 + v_3) & \text{if $\beta \neq 0$} \\
            (\alpha v_1 - \gamma v_3) \wedge v_2 & \text{otherwise}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
    \end{align*}
    are decomposable.
    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
\end{proof}

\begin{example}[Question (b)]
    Consider $V = k^4$. 
    Then the element $w := (e_1 \wedge e_2) + (e_3 \wedge e_4) \in \extpow^2(V)$ is not decomposable. 
\end{example}
\begin{proof}
    Assume it was, then there are $a, b \in k^4$ such that
    \begin{equation*}
        w = \sum_i a_i e_i \wedge \sum_j b_j e_j = \sum_{i < j} (a_i b_j - a_j b_i) (e_i \wedge e_j)
    \end{equation*}
    In other words
    \footnote{Strictly speaking, we require here that $e_i \wedge e_j, i < j$ are linearly independent. However, we will prove this very soon anyway.}
    \begin{equation*}
        a_1b_2 - a_2b_1 = 1, \ a_3b_4 - a_4b_3 = 1, \ a_i b_j - a_j b_i = 0 \ \text{for all $(i, j) \neq (1, 2), (3, 4)$}
    \end{equation*}
    Clearly $a_1 b_2 \neq 0$ or $a_2 b_1 \neq 0$.
    Similarly, have $a_3 b_4 \neq 0$ or $a_4 b_3 \neq 0$.
    As all expressions are symmetric w.r.t swapping $a_1, b_2$ with $a_2, b_1$ and $a_3, b_4$ with $a_4, b_3$, we may assume wlog that $a_1 b_2, a_3 b_4 \neq 0$.

@@

    It is left to show that they are linearly independent.
    Assume
    \begin{equation*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1} \wedge ... \wedge b_{i_d} \bigr) = 0
    \end{equation*}
    Then clearly
    \begin{equation*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) \in U
    \end{equation*}
    where $U$ is the vector space from the definition of $\extpow^d V$.
    So
    \begin{align*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) = &\sum_{j, \ i_1, ..., i_d} \mu_{j, i_1, ..., i_d} \\
        &\Bigl( \bigl( b_{i_1}, ..., b_{i_d} \bigr) + \bigl( b_{i_1}, ..., b_{i_{j - 1}}, b_{i_{j + 1}}, b_{i_j}, b_{i_{j + 2}}, ..., b_{i_d} \bigr) \Bigr)
    \end{align*}
    Note that we can assume wlog that the sum on the right-hand side goes only over $i_1, ..., i_d$ distinct.
    The reason is that the other vectors on the right-hand side are contained in
    \begin{equation*}
       \vspan \{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ not distinct} \}
    \end{equation*}
    which only trivially intersects the space
    \begin{equation*}
        \vspan\{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ distinct} \}
    \end{equation*}
    due to the properties of the free product (the spaces share no basis vectors).

@@

        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \underbrace{\bigl( b_{i_1}, ..., b_{i_d} \bigr)}_{\sgn(\sigma_i) = 1 \ \text{as} \ \sigma_i = \mathrm{id}} = &\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \underbrace{\bigl( \mu_{j, i_1, ..., i_d} + \mu_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} \bigr)}_{=: \mu'_{j, i_1, ..., i_d}} \\

@@

            \lambda_{i_1, ..., i_d} & \text{if $i_1 < ... < i_d, j = 1$} \\

@@

    wlog assume that $b_1, ..., b_m$ are a basis of $W$.

@@

        w = \sum_{i_1 < ... < i_{d - 1} \leq m} \lambda_{i_1, ..., i_{d - 1}} (b_{i_1} \wedge ... \wedge b_{i_{d - 1}})

@@

        =& \sum_{i_1 \leq n, \ i_2 < ... < i_d \leq m} \mu_{i_1} \lambda_{i_2, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})

@@

            \tau_{i_1, ..., i_d} & \text{if $i_1 < i_2$} \\

@@

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
\end{proof}
Now we can see that in general, the exterior product contains not decomposable elements.
\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^d V$.
    Then
    \begin{align*}
        0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
        \overset{*}{=}& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
    \end{align*}
    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).

@@

    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
    To show surjectivity, note that the unit vectors $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
    Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
    \begin{equation*}
        f(e_{i_1} \wedge ... \wedge e_{i_d})_J = \det(A_J(e_{i_1}, ..., e_{i_j})) = \begin{cases}
            0 & \text{if $J \not\subseteq I$} \\
            \pm 1 & \text{if $J \subseteq I$}
        \end{cases}
    \end{equation*}
    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = k^{\{1, ..., k\}^{(d)}}$.

    Finally, note that
    \begin{equation*}
        e_{i_1} \wedge ... \wedge e_{i_d}
    \end{equation*}
    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$ by Lemma~\ref{prop:basis_product_independence}.
    It follows that $\dim(\extpow^d k^n) = \dim(k^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[Question (b)]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[Question (c)]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that for all $2 \leq j \leq l + 1$
    \begin{equation*}
        u_j \wedge ... \wedge u_l \wedge (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    Hence
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}
